Type Refinements for the Working Class

### 2015-11-22 paper.tex
Remark on why pointwise defs are so gnarly, show clean def in the topos
(#7)

>>>>

Then, we say that $\phi$ \emph{globally refines} $\tau$ (written
$\GRefines{\phi}{\tau}$) when for all $\Upsilon$, we have
$\Refines{\Upsilon}{\phi}{\tau}$.

\begin{remark}

  At this point, it should be noted that this is very similar to the semantical
  explanation of typehood given in \cite{martin-lof:1979}, except that we have
  generalized it to a multi-sorted setting, and that we have fibred the entire
  apparatus over collections $\Upsilon$ of symbols.

  In fact, the complexity of the above meaning explanation is an artifact of
  the pointwise style in which we have expressed it. Considered internally to
  the presheaf topos $\Sets^\SCtx$, a refinement is merely a section of the
  object of $\mathfrak{per}(\Exprs_\tau)$, defined internally as a subobject of
  $\Omega^{\Exprs_\tau\times\Exprs_\tau}$:
  \[
    \Define{
      \mathfrak{per}(X)
    }{
      \{ \phi : \Omega^{X\times X}
         \mid
         symmetric(\phi)
         \land transitive(\phi)
      \}
    }
  \]

  So, $\Refines{\Upsilon}{\phi}{\tau}$ obtains just when we have
  $\Member{\phi}{\mathfrak{per}(\Exprs_\tau)(\Upsilon)}$. The benefit of
  explaining such judgments in terms of the presheaf topos is that we do not
  need to deal with the complexities of quantifying over renamings, since this
  is implicit in the definition of the exponential of presheaves,
  \begin{align*}
    \ADefine{
      B^A(\Upsilon)
    }{
      \Hom{\Sets^\SCtx}{
        \Yoneda{\Upsilon}\times A
      }{
        B
      }
    }\\
    &\cong
    \OMode{
      \int_{\Upsilon'}
      (\Upsilon\inj\Upsilon')
      \Rightarrow
      {B(\Upsilon')}^{A(\Upsilon')}
    }
  \end{align*}

\end{remark}
